Title

### 2013-04-01 inc/model_results/lens_charge/lens_charge.tex
added cc notices to the tops of several files
flattened model_results section headings, removing free-space versus forced
tweaks to the lens_charge section

\subsection{Space-charge Effects in Magnetic Lenses} \label{sec:mag_lens_charge}

@@

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for intially oblate ($ \xi ( 0 ) = 0.1 $) or prolate ($ \xi ( 0 ) = 10 $) pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm and a `short' focal length of 6.0mm.
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\ref{fig:compare_shape}).

>>>>

%This work is licensed under the Creative Commons Attribution-NonCommercial-NoDerivs 3.0 United States License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-nd/3.0/us/ or send a letter to Creative Commons, 444 Castro Street, Suite 900, Mountain View, California, 94041, USA.

\section{Space-charge Effects in Magnetic Lenses} \label{sec:mag_lens_charge}

@@

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for intially oblate ($ \xi ( 0 ) = 0.1 $) or prolate ($ \xi ( 0 ) = 10 $) pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm and a `short' focal length of 6.0mm.
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, this simulation again uses the idealistic initial conditions set; the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
As such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsen dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\ref{fig:compare_shape}).
